Circumnuclear Media of Quiescent Supermassive Black Holes

### 2015-07-01 ms.tex
updating figures for new mass loss prescription.

Equation (\ref{eq:conduction}) shows that, even when conduction is
saturated, our neglecting of heat conduction near the stagnation
radius results in at most an order unity correction for causal values
of the saturation parameter $\phi < 0.1$.  Our numerical experiments
which include conductive heating confirm this
($\S\ref{sec:numerical}$).  We do not consider the possibility that
the conduction of heat from the very inner accretion flow can affect
the flow on much larger scales \citep{Johnson+2007}.

@@

...$^{\ddagger}$  & ... & 100 & 0.27 & $ 1.4 \times 10^{ -4 }$ & $ 1.3 \times 10^{ 2

@@

$    10^{ 6 }$ & 600 & 25 & $ 9.4 \times 10^{ -2 }$ & $ 7.4 \times
10^{ -6 }$ & $ 1.1 \times 10^{ 2 }$ & 0.2, 0.6\\

@@

  = 0.2$.  $\ddagger$Calculated with radiative cooling and
  conductivity included, assuming mass loss parameter $\eta = 0.2$ and
  conductivity saturation parameter $\phi = 0.1$.  Solutions including
  radiative cooling were performed for cusp galaxies with $v_w=300 $
  km s$^{-1}$ and core galaxies with $v_w=600 $ km s$^{-1}$ for $\eta$
  = 0.02, 0.2, and 0.6.  Values of $\eta$ resulting in thermally
  unstable solutions are marked in the final column.  Solutions found
  to be thermally unstable for all $\eta \geq 0.02$ are denoted as
  {\bf TI}.

@@

Including thermal conduction, by contrast, results in only minor
changes to our solutions for our fiducial value of the saturation
parameter $\phi = 0.1$, consistent with our analytic expectation
(eq.~[\ref{eq:conduction}]).

@@

Energy and mass input to the CNM by stellar winds is the sum of
contributions from main sequence and post-main sequence populations.
At early times following star formation, energy input is dominated by
core collapse supernovae and by the fast outflows of Wolf-Rayet stars
(e.g., \citealt{VossDiehl+:2009a}).  At later times energy input is
dominated by main sequence winds (e.g.,
\citealt{NaimanSoares-Furtado+:2013a}).  Mass input is also dominated
by massive stars for very young stellar populations, but for most
stellar ages the slow AGB winds of evolved low-mass stars dominate the
mass budget.

@@

If Compton heating acts alone, i.e. $\tilde{v}_{w} = v_{w}^{C}$, then
solving equation (\ref{eq:vC}) for $\tilde{v}_{\rm w}$ yields
\begin{align} v_{w}^{\rm C} \simeq
  \begin{cases} 140 \eta_{0.02}^{0.21}T_{\rm
C,9}^{0.21}\epsilon_{-2}^{0.21} M_{\bullet,8}^{0.16}\,{\rm km\,s^{-1}}
&, \text{core}\\ 95 \eta_{0.02}^{0.34}T_{\rm
C,9}^{0.29}\epsilon_{-2}^{0.29} M_{\bullet,8}^{0.14}\,{\rm km\,s^{-1}}
&, \text{cusp},
  \end{cases}
  \label{eq:vC2}
\end{align} 
Compton heating is thus significant in young stellar populations
with relatively high mass loss rates, e.g. $v_{w}^{\rm C} \gtrsim 300$
km s$^{-1}$ for $\eta \gtrsim 1$.

@@

@@

Shown also for comparison in Figure \ref{fig:bh_growth} (top panel) is
the inflow rate, $\dot{M}$, onto SgrA* calculated by
\citet{Quataert:2004a}.  Also shown is the range of $\dot{M}$ for the
low-luminosity AGN NGC3115 derived through detailed modeling by
\citet{ShcherbakovWong+:2014a}, who find a range of inflow rates
depending on the assumed model for thermal conductivity\footnote{We
  expect this range would be have been smaller had
  \citet{ShcherbakovWong+:2014a} included saturation of the conductive
  flux.}.  The SgrA* rate exceeds our estimate of $\dot{M}$ due to the
average SFH for the same $M_{\bullet}$ by almost two orders of
magnitude.  This discrepancy can in part be understood by the fact
that star formation in the central parsec of the Milky Way cannot be
described as steady-state: feedback is instead dominated by the
stellar winds from the ring of young massive stars of mass $\sim
10^{4}M_{\odot}$ and estimated age $\sim 10$ Myr (e.g.,
\citealt{Schodel+07}).  Such a star formation history is better
described by our impulsive (starburst) scenario, for which the value
of $\eta \sim 100$ at $\tau_{\star} = 10^{7}$ yr
(Fig.~\ref{fig:vwImp}) is a factor of $\sim 100$ times higher than the
value of $\eta \sim 1$ predicted in the average SFH case
(Fig.~\ref{fig:vwSources}, bottom panel).

@@

The unresolved core X-ray luminosities of nearby galactic nuclei
provide a powerful diagnostic of the SMBH accretion rates and how they
vary with SMBH mass and other galaxy properties (e.g., \citealt{Ho08}
and references therein).  Figure~\ref{fig:miller} shows our
predictions for $\langle L_{X} \rangle =\epsilon_X \dot{M} c^2$ as a
function of black hole mass, where $\epsilon_{X} = \alpha\epsilon_{\rm
  rad}\epsilon_{\rm bol}$, $\alpha = 0.1$ accounts for the fraction of
the inflowing matter loss to outflows from the accretion disk,
$\epsilon_{\rm rad}$ is the radiative efficiency of the accreted
matter, and $\epsilon_{\rm bol} = 0.1$ is the assumed bolometric
correction into the measured X-ray band for low luminosity AGN
(\citealt{Ho08}).  In all cases the value of $\langle L_X \rangle$ is
calculated using the accretion rate from the top line of
equation~\eqref{eq:mdot_analytic} with $\Gamma = 0.8$ for $\Mbh < 3
\times 10^7 \Msun$, and $\Gamma=-0.3 \log_{10}
\left(\frac{\Mbh}{3\times 10^7 \Msun}\right)$+0.8 for $\Mbh \geq 3
\times 10^7 \Msun$. This is functional form is designed to
approximately reproduce the behavior of $\Gamma(\Mbh)$ in the
\citet{LauerFaber+:2007a} sample.

@@

\begin{figure*}
\includegraphics[width=\textwidth]{miller.pdf}
\caption{\label{fig:miller} Average nuclear X-ray luminosity, $\langle
  L_X \rangle = \epsilon_X \Mdot c^2$, as a function of SMBH mass.
  Green lines show our prediction in the case of heating due to the
  average SFH for galaxies corresponding to each black hole mass
  (Fig.~\ref{fig:bh_growth}), calculated using $\Gamma = 0.8$ for
  $\Mbh < 3 \times 10^7 \Msun$, and $\Gamma=-0.3 \log_{10}
  \left(\frac{\Mbh}{3\times 10^7 \Msun}\right)$+0.8 for $\Mbh \geq 3
  \times 10^7 \Msun$ derived from the \citet{LauerFaber+:2007a}
  sample.  Shown for comparison are the measurements ({\it black
    stars}) and upper limits ({\it gray triangles}) for $L_X/L_{\rm
    edd}$ values, from the \citet{Miller+15} sample of early-type
  galaxies (a black line shows the best power-law fit $\langle
  L_X/L_{\rm edd}\rangle \propto M_{\bullet}^{\alpha}$, with $\alpha =
  -0.2$).  The left panel is calculated assuming a constant radiative
  efficiency $\epsilon_X=10^{-4} (\epsilon_{\rm bol}/0.1)$, while the
  right hand panel assumes $\epsilon_X= \alpha \epsilon_{\rm
    bol}\epsilon_{\rm rad}$, where $\epsilon_{\rm rad}$ is the
  radiative efficiency of low luminosity accretion disks calculated by
  \citet{Sharma+2007} (eq.~[\ref{eq:efficiency}]) and $\alpha = 0.1$
  is the fraction of the mass inflowing on large scales that reaches
  the SMBH.  Shown for comparison are the X-ray luminosities
  calculated for the maximum thermally-stable accretion rate ({\it
    dashed orange line}; eq.~[\ref{eq:Mdotmax}]); the SN Ia-regulated
  accretion rate ({\it dashed teal line}; eq.~[\ref{eq:eddr_Ia}]), and
  the Compton heating-regulated accretion rate ({\it dashed pink
    line}; eq.~[\ref{eq:MdotCa}]), again all calculated for the
  average SFH corresponding to each SMBH mass.}
\end{figure*}

@@

  \item In the vicinity of the stagnation radius including the effects
    of heat transport by electron conduction results in at most order
    unity changes to the key properties of the flow (e.g. stagnation
    radius, mass accretion rate, and thermal stability) for causal
    values of the conduction saturation parameter $\phi < 0.1$
    (eq.~[\ref{eq:conduction}]). However, in principle heat conduction
    of heat from the very inner accretion flow can affect the solution
    properties on much larger scales \citep{Johnson+2007}. Angular
    momentum is also unlikely to invalidate our spherically symmetric
    model on large scales, given observationally inferred rotation
    rates of galactic nuclei near the stagnation radius
    ($\S\ref{sec:rotation}$).

>>>>

Equation (\ref{eq:conduction}) shows that, even when conduction is
saturated, our neglecting of heat conduction near the stagnation
radius results in at most an order unity correction for causal values
of the saturation parameter $\phi < 0.1$.  Our numerical experiments
which include conductive heating confirm this
($\S\ref{sec:numerical}$).  We do not consider the possibility that
the conduction of heat from the inner accretion flow can affect
the flow on much larger scales \citep{Johnson+2007}.

@@

...$^{\ddagger}$  & ... & 100 & 0.07 & $ 2.8 \times 10^{ -5 }$ & $ 4.7 \times 10^{ 2

@@

%$    10^{ 6 }$ & 600 & 25 & $ 9.4 \times 10^{ -2 }$ & $ 7.4 \times
%10^{ -6 }$ & $ 1.1 \times 10^{ 2 }$ & 0.2, 0.6\\
$    10^{ 6 }$ & 600 & 25 & $\mathbf{TI}$ & $\mathbf{TI}$ & $\mathbf{TI}$  & \\

@@

  = 0.2$.  $\ddagger$Calculated with conductivity and cooling
  included, assuming mass loss parameter $\eta = 0.2$ and conductivity
  saturation parameter $\phi = 0.1$.  Solutions including radiative
  cooling were performed for cusp galaxies with $v_w=300 $ km s$^{-1}$
  and core galaxies with $v_w=600 $ km s$^{-1}$ for $\eta$ = 0.02,
  0.2, and 0.6.  Values of $\eta$ resulting in thermally unstable
  solutions are marked in the final column.  Solutions found to be
  thermally unstable for all $\eta \geq 0.02$ are denoted as {\bf TI}.

@@

Including thermal conduction, by contrast, results in only order unity
changes to our solutions for our fiducial value of the saturation
parameter $\phi = 0.1$, consistent with our analytic expectations
(eq.~[\ref{eq:conduction}]). However, we found that for runs which
included conductivity the stagnation radius varied with the location
of the inner grid boundary: as the boundary is moved inwards more heat
can be conducted outwards from deeper in the gravitational potential
well of the black hole. We expect conductivity would begin to have a
significant effect for an inner boundary $\lsim 0.01 \rs$ (the
conductive run in Table~\ref{table:models} has an inner grid boundary
at $\sim 0.03 \rs$). However, it is not clear physically if the
magnetic field could remain coherent over so many decades in radius.

@@

Energy and mass input to the CNM by stellar winds is the sum of
contributions from main sequence and post-main sequence populations.
t early times following star formation, energy input is dominated by
core collapse supernovae and by the fast outflows of Wolf-Rayet stars
(e.g., \citealt{VossDiehl+:2009a}).  At later times energy input is
dominated by main sequence winds (e.g.,
\citealt{NaimanSoares-Furtado+:2013a}).  Mass input is also dominated
by massive stars for very young stellar populations, but for most
stellar ages the slow AGB winds of evolved low-mass stars dominate the
mass budget.

@@

If Compton heating acts alone, i.e. $\tilde{v}_{w} = v_{w}^{C}$, then
solving equation (\ref{eq:vC}) for $\tilde{v}_{\rm w}$ yields
\begin{align} v_{w}^{\rm C} \simeq
  \begin{cases} 140 \eta_{0.02}^{0.21}T_{\rm
C,9}^{0.21}\epsilon_{-2}^{0.21} M_{\bullet,8}^{0.16}\,{\rm km\,s^{-1}}
&, \text{core}\\ 95 \eta_{0.02}^{0.34}T_{\rm
C,9}^{0.29}\epsilon_{-2}^{0.29} M_{\bullet,8}^{0.14}\,{\rm km\,s^{-1}}
&, \text{cusp},
  \end{cases}
  \label{eq:vC2}
\end{align} 
ompton heating is thus significant in young stellar populations
with relatively high mass loss rates, e.g. $v_{w}^{\rm C} \gtrsim 300$
km s$^{-1}$ for $\eta \gtrsim 1$.

@@

% \begin{table*}
% \begin{threeparttable}
% \begin{minipage}{18cm}
% \caption{Comparison of CNM gas density at r=10$^{18}$ between our
%   model and existing constraints on the gas density on this scale for
%   the Milky Way from Chandra x-ray observations (first row) and from
%   modeling the radio light curve in the Swift J1644 transient (second row).}
% \begin{tabular}{lll}
%   {System} &  {Model} & {Comparison} \\
%   %\hline
%   Milky Way & 3 cm${-3}$ & 26 cm$^{-3}$\\
%   Swift J1644+57 & 5 cm$^{-3}$ & 0.8 cm$^{-3}$\\
%   %\hline
% \label{table:compare}  
% \end{tabular}
% % \begin{tablenotes}
% %   Model estimate has been corrected for the fact the analytic
% %   prescription underestimates gas density. This corresponds to model
% %   estimate for core galaxies.
% % \end{tablenotes}
% \end{minipage}
% \end{threeparttable}
% \end{table*}

@@

Shown also for comparison in Figure \ref{fig:bh_growth} (top panel) is
the inflow rate, $\dot{M}$, onto SgrA* calculated by
\citet{Quataert:2004a} and by \citet{Cuadra+2008}.  Also shown is the
range of $\dot{M}$ for the low-luminosity AGN NGC3115 derived through
detailed modeling by \citet{ShcherbakovWong+:2014a}, who find a range
of inflow rates depending on the assumed model for thermal
conductivity.  The inflow rate SgrA* estimated from
\citet{Quataert2004} exceeds our estimate of $\dot{M}$ due to the
average SFH for the same $M_{\bullet}$ by almost two orders of
magnitude. This is because the mass source term in
\citet{Quataert2004} exceeds ours by several orders of magnitude.
The star formation in the central parsec of the Milky Way cannot be
described as steady-state: feedback is instead dominated by the
stellar winds from the ring of young massive stars of mass $\sim
10^{4}M_{\odot}$ and estimated age $\sim 10$ Myr (e.g.,
\citealt{Schodel+07}).  Such a star formation history is better
described by our impulsive (starburst) scenario, for which the value
of $\eta \sim 100$ at $\tau_{\star} = 10^{7}$ yr
(Fig.~\ref{fig:vwImp}) is a factor of $\sim 100$ times higher than the
value of $\eta \sim 1$ predicted in the average SFH case
(Fig.~\ref{fig:vwSources}, bottom panel).

However, simulations by \citet{Cuadra+2006} find that
the inflow rate for Sgr A* is reduced by up to an order of magnitude
compared to the result in \citet{Quataert2004} when the discreteness
and disk geometry of stellar sources is taken into account.

@@

The unresolved core X-ray luminosities of nearby galactic nuclei
provide a powerful diagnostic of the SMBH accretion rates and how they
vary with SMBH mass and other galaxy properties (e.g., \citealt{Ho08}
and references therein).  Figure~\ref{fig:miller} shows our
predictions for $\langle L_{X} \rangle =\epsilon_X \dot{M} c^2$ as a
function of black hole mass, where $\epsilon_{X} = \alpha\epsilon_{\rm
  rad}\epsilon_{\rm bol}$, $\alpha = 0.1$ accounts for the fraction of
the inflowing matter loss to outflows from the accretion disk,
$\epsilon_{\rm rad}$ is the radiative efficiency of the accreted
matter, and $\epsilon_{\rm bol} = 0.1$ is the assumed bolometric
correction into the measured X-ray band for low luminosity AGN
(\citealt{Ho08}).  In all cases the value of $\langle L_X \rangle$ is
calculated using the accretion rate from the top line of
equation~\eqref{eq:mdot_analytic} with $\Gamma = 0.7$ for $\Mbh < 4
\times 10^7 \Msun$, and $\Gamma=-0.3 \log_{10}
\left(\frac{\Mbh}{4\times 10^7 \Msun}\right)$+0.7 for $\Mbh \geq 4
\times 10^7 \Msun$. This is functional form is designed to
approximately reproduce the behavior of $\Gamma(\Mbh)$ in the
\citet{LauerFaber+:2007a} sample.

@@

\begin{figure*}
\includegraphics[width=\textwidth]{miller.pdf}
\caption{\label{fig:miller} Average nuclear X-ray luminosity, $\langle
  L_X \rangle = \epsilon_X \Mdot c^2$, as a function of SMBH mass.
  Green lines show our prediction in the case of heating due to the
  average SFH for galaxies corresponding to each black hole mass
  (Fig.~\ref{fig:bh_growth}), calculated using $\Gamma = 0.7$ for
  $\Mbh < 4 \times 10^7 \Msun$, and $\Gamma=-0.3 \log_{10}
  \left(\frac{\Mbh}{4\times 10^7 \Msun}\right)$+0.7 for $\Mbh \geq 4
  \times 10^7 \Msun$ derived from the \citet{LauerFaber+:2007a}
  sample.  Shown for comparison are the measurements ({\it black
    stars}) and upper limits ({\it gray triangles}) for $L_X/L_{\rm
    edd}$ values, from the \citet{Miller+15} sample of early-type
  galaxies (a black line shows the best power-law fit $\langle
  L_X/L_{\rm edd}\rangle \propto M_{\bullet}^{\alpha}$, with $\alpha =
  -0.2$).  The left panel is calculated assuming a constant radiative
  efficiency $\epsilon_X=10^{-4} (\epsilon_{\rm bol}/0.1)$, while the
  right hand panel assumes $\epsilon_X= \alpha \epsilon_{\rm
    bol}\epsilon_{\rm rad}$, where $\epsilon_{\rm rad}$ is the
  radiative efficiency of low luminosity accretion disks calculated by
  \citet{Sharma+2007} (eq.~[\ref{eq:efficiency}]) and $\alpha = 0.1$
  is the fraction of the mass inflowing on large scales that reaches
  the SMBH.  Shown for comparison are the X-ray luminosities
  calculated for the maximum thermally-stable accretion rate ({\it
    dashed orange line}; eq.~[\ref{eq:Mdotmax}]); the SN Ia-regulated
  accretion rate ({\it dashed teal line}; eq.~[\ref{eq:eddr_Ia}]), and
  the Compton heating-regulated accretion rate ({\it dashed pink
    line}; eq.~[\ref{eq:MdotCa}]), again all calculated for the
  average SFH corresponding to each SMBH mass.}
\end{figure*}

@@

  \item In the vicinity of the stagnation radius including the effects
    of heat transport by electron conduction results in at most order
    unity changes to the key properties of the flow (e.g. stagnation
    radius, mass accretion rate, and thermal stability) for causal
    values of the conduction saturation parameter $\phi < 0.1$
    (eq.~[\ref{eq:conduction}]). However, in principle heat conduction
    of heat from the inner accretion flow can affect the solution
    properties on much larger scales \citep{Johnson+2007}. For
    example, \citet{Tanaka+2006} find that conductivity can contribute
    to driving bipolar outflows.

    Angular momentum is likely unimportant for large scale flow
    properties ($\S\ref{sec:rotation}$). However, it will become
    important on small scales, where gas stopped by a centrifugal
    barrier and unable to cool could drive a bipolar outflow.

### 2015-07-01 windheat.tex
updating figures for new mass loss prescription.

In the case of a single impulsive burst of star formation, the mass
and energy injection rate per unit stellar mass at time $t$ after the
burst are given, respectively, by
\begin{align} 
  \dot{\bar{m}}(t) &= \frac{\Delta M(t) \mu|_{M_{\rm TO}(t)}
    \left|\dot{M}_{\rm TO}(t)\right| + f_{\rm MS} \int_{m_0}^{m_{\rm
        T}(t)} \dot{m}(\Mstar, t) \mu|_{\Mstar} {\rm d}\Mstar
  }{\bar{m}_*}\label{eq:mdotImp}
  \\
  \dot{\bar{e}}(t) &=f_{\rm OB} \, \dot{e}_{\rm OB}(t)+ f_{\rm MS}
  \int_{m_0}^{m_{\rm T}(t)} \frac{\vw^2(\Mstar, t) \dot{m}(\Mstar, t)
    \mu|_{\Mstar} {\rm d}\Mstar}{\bar{m}_*},
  \label{eq:edotImp}
\end{align} 
In the top line, the first and second terms correspond to contributions
from main sequence (MS) stars and post-main sequence (PMS) stars,
respectively. Here $\mu$ is the IMF, which we take to be of the
Salpeter form $\mu|_{\Mstar} \propto M_{\star}^{-2.35}$, truncated at
$m_0 = 0.1 \Msun$ on the low mass end and at $100 \Msun$ on the high
mass end, where $\bar{m}_*$ = 0.35 $\Msun$ is the corresponding mean
stellar mass. In practice the contribution of main sequence winds to
the mass budget is negligible, and so we drop the second term in
equation~\eqref{eq:mdotImp}.

The first term in equation~\eqref{eq:edotImp} corresponds energy
injection from massive O \& B stars, while the second term accounts
for energy injection from stars on the lower main sequence. Both terms
have a thermalization efficiency, $f$, which we talk to be $1$. Note
we do not account for energy from Type II supernovae. However, the
mass injection from type II supernovae is implicitly included in the
first term of equation~\eqref{eq:mdotImp}

>>>>

In the case of a single impulsive burst of star formation, the mass
and energy injection rate per unit stellar mass at time $t$ after the
burst are given, respectively, by
\begin{align} 
  \dot{\bar{m}}(t) &= f_{\rm TO} \dot{m}_{\rm TO} + f_{\rm OB}
  \dot{m}_{\rm OB}\\
% + f_{\rm MS} \int_{m_0}^{m_{\rm T}(t)}
%$  \dot{m}(\Mstar, t) \mu|_{\Mstar} {\rm d}\Mstar
%}{\bar{m}_*}\label{eq:mdotImp}
\dot{\bar{e}}(t) &=f_{\rm OB} \, \dot{e}_{\rm OB}(t)+ f_{\rm MS}
\int_{m_0}^{m_{\rm T}(t)} \frac{\vw^2(\Mstar, t) \dot{m}(\Mstar, t)
  \mu|_{\Mstar} {\rm d}\Mstar}{\bar{m}_*},
  \label{eq:edotImp}
\end{align}

In the top line, the first term corresponds to mass injection due
winds from post-main sequence stars. The second term corresponds to
mass injection due to stellar winds from massive and O and B
stars. For the latter we use population synthesis calculations by
\citet{VossDiehl+:2009a}. From the bottom panel of their Figure 7, the
stellar wind mass loss rate per massive star can be approximated to within
a factor of a few by

\begin{equation}
\dot{\mathcal{M}}=10^{-5.4} \left(\frac{t}{4\times 10^6 {\rm
       yr}}\right)^{-3} 4 {\, \rm Myr} \leq t \leq 40 {\, \rm Myr}. 
\end{equation}

and 0 for all later times. We neglect the mass injection due to
stellar winds for times $t\lsim 4$ Myr. $\dot{m}_{\rm OB}=f_{8}
\dot{\mathcal{M}}/\bar{m}_{\star}$, where $f_{8} =2.6 \times 10^{-3}$
is the fraction of the stellar mass with $M_{\star} > 8M_{\odot}$ and
$m_{\star}=0.35 \Msun$ is the mean stellar mass for our assumed
Salpeter IMF, $\mu\sim M_\star^{-2.35}$.

For the mass loss rate from post-main sequence winds, we take

\begin{equation}
  \dot{m}_{\rm TO}=\frac{\Delta M(t) |\dot{M}_{\rm TO}(t)|
    \mu|_{M_{\rm TO}(t)}}{\bar{m}_{\star}}  \,\,  t \geq {\rm 40 Myr},
\end{equation}

and 0 for earlier times. By truncating $dot{m}_{\rm TO}$ at 40 Myr, we
are ignoring the non-steady mass injection by type II supernovae.

The first term in equation~\eqref{eq:edotImp} corresponds energy
injection from massive O \& B stars, while the second term accounts
for energy injection from stars on the lower main sequence. Both terms
have a thermalization efficiency, $f$, which w e talk to be $1$. Note
we do not account for energy from Type II supernovae.
